\Large Carryover effects in free recall reveal how past experiences influence memories of future experiences

### 2023-01-17 paper/main.tex
added author contributions, data and code availability, and acknowledgements statements

>>>>

\subsection*{Author contributions}

Conceptualization: JRM and ACH. Methodology: JRM and ACH. Software: JRM, KZ,
PCF, CEF, and ACH. Analysis: JRM, PCF, and ACH. Data collection: KZ, EW, PCF,
MRL, AMF, BJB, and CEF. Data curation and management: KZ, EW, PCF, MRL, ACH.
Writing (original draft): JRM. Writing (review and editing): KZ, EW, PCF, MRL,
AMF, BJB, CEF, and ACH. Supervision: JRM and ACH. Project administration: KZ,
EW, and PCF. Funding acquisition: JRM.

\subsection*{Data and code availability}

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses may be found at
https://github.com/ContextLab/FRFR-analyses. Code for running the non-adaptive
expermental conditions may be found at
https://github.com/Context\-Lab/efficient-learning-code. Code for running the
adaptive experimental condition may be found at
https://github.com/ContextLab/adaptiveFR. We have also released an associated
Python toolbox for analyzing free recall data, which may be found at
https://cdl-quail.read\-the\-docs.io/\-en/\-latest/.

\subsection*{Acknowledgements}

We acknowledge useful discussions, assistance in setting up an earlier version
of this study, and assistance with some of the data collection efforts from
Rachel Chacko, Joseph Finkelstein, Sheherzad Mohydin, Lucy Owen, Gal Perlman,
Darya Romanova, Jake Rost, Jessica Tin, Marisol Tracy, and Peter Tran. Our work
was supported in part by NSF CAREER Award Number 2145172 to JRM. The content
is solely the responsibility of the authors and does not necessarily represent
the official views of our supporting organizations. The funders had no role in
study design, data collection and analysis, decision to publish, or preparation
of the manuscript.
